Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-07-09 Draft/draft.tex
changes to main text and reference list

% Square root of epsilon
\newcommand{\ep}{\epsilon}
\newcommand{\se}{\sqrt{\epsilon}}
\newcommand{\qe}{\epsilon^{1/4}}
\newcommand{\sd}{\sqrt{d}}
\newcommand{\sr}{\sqrt{r}}
\newcommand{\qd}{d^{1/4}}

@@

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
\cite{miller2017,fu2018,eat2018}.
\hfc{Which DIQKD paper should I cite?}
\carl{Two possible papers that you could cite are Mayer Yao 1998 (which originated the idea of self-testing as far as I know, and mentions QKD) and my paper (miller2017, which you've already cited --- indeed it uses the concept of self-testing).  Also you should check Vazirani-Vidick's 2014 PRL paper to see if it mentions self-testing at all.  (It was the first to fully prove DI-QKD.)}

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2016parallel, lowdegree}. 
\carl{I believe the first to prove robust self-testing of a single EPR pair was McKague-Yang-Scarani 2012.}
Self-testing general $d$-dimensional EPR pairs is a harder task.
Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
by constructing an explicit correlation of size $\Theta(d^2)$ that can be used for self-testing,
which is the only result about the general $d$-dimensional case so far.
However, proving the robustness of the correlation remains an open problem. 
Without robustness, we cannot infer anything about a quantum strategy if
the produced correlation deviates from the ideal correlation, no matter how small the 
deviation is.

@@

\begin{definition}[Group presentation]
    Given a set $S$, let $\mathcal{F}(S)$ be the free group generated by $S$ and $R$ be a subset of $\mathcal{F}(S)$.
    Then $\ip{S:R}$ denotes the quotient of $\mathcal{F}(S)$
    by the normal subgroup generated by $R$.
    If the group $G$ is isomorphic to $\ip{S:R}$,
    then we say $G$ 
    has a presentation $\ip{S:R}$. 
\end{definition}
If both sets $S$ and $R$ are finite, then we say the group $G = \ip{S:R}$ is \emph{finitely-presentable}.
The elements of $S$ are the \emph{generators} and the elements
of $R$ are the \emph{relations}.
When we refer to an equation
of the form $a = b$ with $a, b \in \mathcal{F} ( S )$ as a ``relation,'' 
it is understood 
that we mean the element $ab^{-1} 
\in R$.
\hf{ There are two types of relations that we will be working with.
} 
Considering \hf{a subset of generators} $\{ s_j \}_{j=1}^n \subset S$ \hf{such that $s_{j_1} \neq s_{j_2}$ if $j_1 \neq j_2$},
the relations of the form $\Pi_{j=1}^n s_j  = e$, where $e$ is the identity element, are called 
\emph{linear relations};
and the relations of the form
$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   \carl{This last sentence
needs to be made more precise (e.g., are
repetitions allows in the linear relations)?}
\hfc{I thought the fact that $\{s_j\}$ is a subset of $S$ guarantees that there will be no repetitions in a linear relation.}
\begin{definition}
    A representation of $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
\end{definition}
The last concept of group theory that we need is group embedding.
\begin{definition}[Group embedding]
    An embedding of $G$ into $K$ is an injective group homomorphism: $\phi: G \rightarrow K$.
\end{definition}
%-----------------------------------------
\subsection{Nonlocal games}
%-----------------------------------------
In a nonlocal game, there are two players, Alice and Bob and each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function.

@@

The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
into the solution group of a binary linear system game.  
We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group
\begin{align}
    \Pg = \ip{u,o:uou^{-1} = o^r},
\label{pgroup}
\end{align}
for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
Since the steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed in the proofs of Proposition~$33$, Lemma~$29$ and
Proposition $27$ of Ref.~\cite{slofstra2017}, 
we defer the formal statements of the embedding procedure till \cref{sec:embedding},
but give the idea behind this procedure in \cref{sec:embed_idea}. 
In \cref{sec:lsg_def}, we define $\Gamma$ and introduce how to
construct $\LS(r)$ from $\Gamma$.
We also highlight a few operators from a finite-dimensional representation of $\Gamma$.
The representation will be used later to build the ideal strategy.

%----------------------------------------
\subsection{A sketch of the procedure
for constructing $\LS ( r )$}
\label{sec:embed_idea}
%----------------------------------------
The group $\Pg$ (see equation (\ref{pgroup} above) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}), which is the
solution group of $\LS ( r )$.  
Thus we obtain a chain of embeddings:
\begin{align}
\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow
\Gamma.
\end{align}
The purposes of introducing each intermediate
group are explained below.

First observe that the generators $u$ and $o$ have arbitrary order in $\Pg$. However, all the generator of a solution
group are of order-$2$, so it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$
to a single generator. 
\hf{This is the reason why we first embed $\Pg$ into $\Pg_0 := \ip{S_0:R_0}$, where all the generators in $S_0$ are of 
order-$2$ and all the relations in $R_0$ are conjugacy relations.
The generators in $S_0$ are $a_i$ for $i=1 \dots r+5$.
The special generators are $a_1, a_2, a_3$ and $a_4$ because the product $a_1a_2$ behaves similarly as $o$
and the product $a_3a_4$ behaves similarly as $u$.}
\carl{[You should probably
say somewhere that $\mathcal{P}_0$ is defined
by conjugacy relations (since it seems like you're assuming that the reader knows that).]}
\hfc{Fixed.}
Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$ (see \cref{prop:g0}), so
a homomorphism: $\Pg \rightarrow\Pg_0$  that maps $o$ to $a_1a_2$ and $u$ to $a_3a_4$ is an embedding of $\Pg$ into $\Pg_0$
by Proposition $33$ of Ref.~\cite{slofstra2017}.
To better characterize the conjugacy relations in $R_0$, we introduce $C(r)$ defined in \cref{eq:cr}
of tuples $(i,j,k)$ such that $(i,j,k) \in C(r)$ if and only if $a_ia_ja_i = a_k$ is in $R_0$.

\hf{Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$
and $R_1$ consists of both linear relations and conjugacy relations.
The special properties of $S_1$ and $R_1$ are
\begin{enumerate}
    \item $s_is_js_i = s_k \in R_1$ implies that there exists a generator
$s' \in S_1$ such that $s' s_j s_k = e \in R_1$;
    \item every relation in $R_0$ can be derived from $R_1$.
\end{enumerate}
Note that $s'$ can be seen as an auxiliary generator such that
its existence implies that $s_j$ and $s_k$ commute, because
\begin{align*}
    [s_j, s_k] = s_j s_k s_j s_k = (s')^2 = e.
\end{align*}
Ensuring the conjugacy relations are associating one generator to another one which 
commutes with it is the purpose of introducing $\Pg_1$. 
It makes the construction of a finite-dimension representation of $\Gamma$ from
a finite-dimension representation of $\Pg_1$ easier.}
\carl{[that's vague -- either explain it or don't say it]}
\hfc{How about now?} 
Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
for each generator $a_i \in S_0$.
There is also a special generator $f_0 \in S_1$ such that
\begin{align*}
    a_i = b_ic_i = f_0d_i. 
\end{align*}
The relation $a_i = b_ic_i$ guarantees that $b_i$ commutes
with $c_i$.
The generators $b_i$ and $c_i$ are also related by a conjugacy relation
\begin{align*}
    c_i = f_0 b_i f_0. 
\end{align*}
For each $(i,j,k) \in C(r)$, 
$S_1$ contains an auxiliary generator $h_{jk}$, and
$R_1$ 
contains a conjugacy relation 
\begin{align*}
    d_ib_jd_i = c_k,
\end{align*}
and a linear relation
\begin{align*}
    h_{jk}b_jc_k = e.
\end{align*}
The introduction of $h_{jk}$ helps us to deduce that 
$b_j$ commutes with $c_k$.
Hence, every conjugacy relation in $R_1$ is either of the form
$f_0b_if_0 = c_i$ for $1 \leq i \leq r+5$, or
$d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
\hf{From the conjugacy relations in $R_1$, it can be proven that
\begin{align*}
    d_ic_jd_i = b_k \text{ for each } (i,j,k) \in C(r).
\end{align*}
Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
the conjugacy relations deduced above. For details, we refer to the 
proof of \cref{prop:g0g1}.}
\carl{It would be good to explain (or at least reiterate) that these relations allow us to recover the conjugacy relations in $\mathcal{R}_0$.}
\hfc{How about now?}

@@

In the last step, we can construct $\Gamma:= \ip{S:R}$ with $S_1 \subset S$, in a way such that
$\Gamma$ only has linear relations, and the linear relations can be combined
to recover the conjugacy relations in $R_1$.
We demonstrate how relation $f_0 b_1 f_0 = c_1$ is embedded in
$6$ linear relations of $R$ as an example. 
The other conjugacy relations of $\Pg_1$ are embedded in linear relations in a similar way.
We introduce auxiliary generators $f_1, f_2$ and $\{p_{1,j}\}_{j=1}^5$ and they satisfy the linear relations:
\begin{align*}
    &f_0 f_1 f_2 = e && b_1 f_2 p_{1,1} = e && p_{1,1} p_{1,2} p_{1,3} = e\\
	&f_0 p_{1,3} p_{1,4} = e && c_1 p_{1,4} p_{1,5} = e \quad f_1 p_{1,2} p_{1,5} = e.
\end{align*}
For details about how the linear relations above
can be combined to recover $f_0b_1f_0 = c_1$, we refer to \cref{sec:embedding}.
A representation of $\Gamma$ can also be built upon
the representation $\Psi_1$ of $\Pg_1$.
We denote the representation of $\Gamma$ by $\Psi$ and
it is defined on $\C^2 \x \C^2 \x \calH$ such that
\begin{align*}
    \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
    s \in S_1.
\end{align*}
In particular, it means that for each $a_i \in S_0$
\begin{align*}
    \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
\end{align*}
Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
by Lemma $15$ of Ref.~\cite{slofstra2017}.

%----------------------------------------
\subsection{Formal definitions}
\label{sec:lsg_def}
%----------------------------------------
We define the solution group of the linear system game $\LS(r)$ first, which is constructed following the steps
described in the previous subsection.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{J\} \cup \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
set of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ JsJs = e \vert s \in S\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
The group $\Gamma$ is a group with the presentation
$\ip{S:R}$.
\carl{[If you're really going to claim
that this is a complete definition, maybe you should write out the set $C$ somewhere as well?]}
\end{definition}
\hfc{I pointed out in the previous subsection that the definition of $C(r)$ is in the Appendix along with the definition of $\Pg_0$. 
Since $C(r)$ is defined by $\Pg_0$, a stand-alone definition of $C(r)$
will only confuse the reader. Are you suggesting that we don't make this a definition?}

@@

In the next three subsections, we analyze the implication of an approximate strategy to pass the 
three tests given in \cref{sec:full_test}.

%------------------------------------------------------------------------------------------
\subsection{Implication of winning $\LS(r)$}
\label{sec:imp_lct}
%------------------------------------------------------------------------------------------
In the first half of this subsection, we use $(i,s)$ to denote the question pair so that Alice gets equation number $i$ and Bob gets a variable label $x(s)$ for some $s \in S$. For simplicity, we let Bob get the generator $s$ instead.

>>>>

% Square root of epsilon
\newcommand{\ep}{\epsilon}
\newcommand{\se}{\sqrt{\epsilon}}
\newcommand{\qe}{\epsilon^{1/4}}
\newcommand{\sd}{\sqrt{d}}
\newcommand{\sr}{\sqrt{r}}
\newcommand{\qr}{r^{1/4}}
\newcommand{\qd}{d^{1/4}}

@@

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
\carl{Two possible papers that you could cite are Mayer Yao 1998 (which originated the idea of self-testing as far as I know, and mentions QKD) and my paper (miller2017, which you've already cited --- indeed it uses the concept of self-testing).  Also you should check Vazirani-Vidick's 2014 PRL paper to see if it mentions self-testing at all.  (It was the first to fully prove DI-QKD.)}
\hfc{checked.}

The case of self-testing $2$-dimensional EPR pair is fully understood.
The techniques for robustly self-testing one EPR pair is 
first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
Ref.~\cite{yang2013} started to think about how to robustly self-testing large dimensional maxially entangled states.
Its ideas are realized later in Ref.~\cite{coladan2017all}, which proved that all pure bipartite entangled state 
can be self-tested.
One can also self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
The most efficient way uses $O(\log n)$ bits question and
answers to self-test $n$ copies of $2$-dimensional EPR
pair \cite{lowdegree}.
\carl{I believe the first to prove robust self-testing of a single EPR pair was McKague-Yang-Scarani 2012.}
\hfc{Got it.}
Self-testing general $d$-dimensional EPR pairs is a harder task.
Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
by constructing an explicit correlation of size $\Theta(d^2)$ that can be used for self-testing,
which is the only result about the general $d$-dimensional case so far.
However, proving the robustness of the correlation remains an open problem. 
Without robustness, we cannot infer anything about a quantum strategy if
the produced correlation deviates from the ideal correlation, no matter how small the 
deviation is.

@@

\begin{definition}[Group presentation]
    Given a set $S$, let $\mathcal{F}(S)$ be the free group generated by $S$ and $R$ be a subset of $\mathcal{F}(S)$.
    Then $\ip{S:R}$ denotes the quotient of $\mathcal{F}(S)$
    by the normal subgroup generated by $R$.
    If the group $G$ is isomorphic to $\ip{S:R}$,
    then we say $G$ 
    has a presentation $\ip{S:R}$. 
If both sets $S$ and $R$ are finite, then we say the group $G = \ip{S:R}$ is \emph{finitely-presentable}.
The elements of $S$ are the \emph{generators} and the elements
of $R$ are the \emph{relations}.
When we refer to an equation
of the form $a = b$ with $a, b \in \mathcal{F} ( S )$ as a ``relation,'' 
it is understood 
that we mean the element $ab^{-1} 
\in R$.
\hf{ There are two types of relations that we will be working with.
} 
Considering \hf{a subset of generators} $\{ s_j \}_{j=1}^n \subset S$ \hf{such that $s_{j_1} \neq s_{j_2}$ if $j_1 \neq j_2$},
the relations of the form $\Pi_{j=1}^n s_j  = e$, where $e$ is the identity element, are called 
\emph{linear relations};
and the relations of the form
$s_i s_j s_i^{-1} = s_k$ for some $i \neq j$ are called \emph{conjugacy relations}.   \carl{This last sentence
needs to be made more precise (e.g., are
repetitions allows in the linear relations)?}
\hfc{I thought the fact that $\{s_j\}$ is a subset of $S$ guarantees that there will be no repetitions in a linear relation.}
There are two special types of groups that we will work with in \cref{sec:lsg}. We give the definitions below.
    \label{def:spe_conj_grp}
    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
    Let
        \Gamma = \ip{\{s_i\}_{i \in [n]}  :
        \{s_i^2=e\}_{i\in [n]} \cup 
        \{ s_i s_j s_i = s_k\}_{(i,j,k)\in C}}.
    We say a group is a conjugacy group if it has a presentation of this form. 
A conjugacy group is a special case of what Slofstra defined as 
a linear-plus-conjugacy group (Definition $26$ of Ref.~\cite{slofstra2017}). The difference is that a conjugacy group does not have linear relations. The next definition follows the 
definition of a nice linear-plus-conjugacy group (Definition $28$ of \cite{slofstra2017}).
    \label{def:nice_conj_grp}
    Suppose $C \subset [n] \times [n] \times [n]$, where $[n] = \{1,2 \dots n\}$. 
    Let 
        \Gamma = \ip{\{s_i\}_{i \in [n]} \cup \{s_{jk}\}_{(i,j,k)\in C} :
        \{s_i^2=e\}_{i\in [n]} \cup 
        \{s_{jk}^2 = e, s_is_js_i = s_k, s_{jk}s_js_k = e\}_{(i,j,k)\in C}}.
    We say a group is a nice conjugacy group if it has a presentation of this form. 
The relation $s_{jk} s_js_k = e$ implies that $s_j$ commutes with $s_k$
    [s_j, s_k] = s_js_ks_js_k = s_{jk}^2 = e.
Next we give the definition of a group representation. 
    A representation of $G$ on the finite Hilbert space $\calH$ is a homomorphism from $G$ to the group of invertible linear operators on $\calH$. 
The last concept of group theory that we need is group embedding.
\begin{definition}[Group embedding]
    An embedding of $G$ into $K$ is an injective group homomorphism: $\phi: G \rightarrow K$.
%-----------------------------------------
\subsection{Nonlocal games}
%-----------------------------------------
In a nonlocal game, there are two players, Alice and Bob and each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and her answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function.

@@

The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
into the solution group of a binary linear system game.  
We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group
\begin{align}
    \Pg = \ip{u,o:uou^{-1} = o^r},
\label{eq:pgroup}
\end{align}
for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
Since the steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed in the proofs of Proposition~$33$, Lemma~$29$ and
Proposition $27$ of Ref.~\cite{slofstra2017}, 
we defer the formal statements of the embedding procedure till \cref{sec:embedding},
but sketch this procedure in \cref{sec:embed_idea}. 
In \cref{sec:lsg_def}, we define $\Gamma$ and introduce how to
construct $\LS(r)$ from $\Gamma$.
We also highlight a few operators from a finite-dimensional representation of $\Gamma$.
The representation will be used later to build the ideal strategy.

%----------------------------------------
\subsection{A sketch of the procedure
for constructing $\LS ( r )$}
\label{sec:embed_idea}
%----------------------------------------
The group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}), which is the
solution group of $\LS ( r )$.  
Thus we obtain a chain of embeddings:
\begin{align}
\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow
\Gamma.
\end{align}
The purposes of introducing each intermediate
group are explained below.

The group $\Pg_0 := \ip{S_0:R_0}$ is a 
conjugacy group, which is defined in \cref{def:spe_conj_grp}. 
The generators in $S_0$ are $a_i$ for $i=1 \dots r+5$.
The purpose of this step is to embed $\Pg$ into a group where all the
generators are of order-$2$, because
it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single generator. On the other hand, 
a homomorphism from $\Pg_0$ to a solution group can be easier to find.
The special generators of $\Pg_0$ are $a_1, a_2, a_3$ and $a_4$ because the product $a_1a_2$ behaves similarly as $o$
and the product $a_3a_4$ behaves similarly as $u$.
Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$ (see \cref{prop:g0}), so
a homomorphism: $\Pg \rightarrow\Pg_0$  that maps $o$ to $a_1a_2$ and $u$ to $a_3a_4$ is an embedding of $\Pg$ into $\Pg_0$
by Proposition $33$ of Ref.~\cite{slofstra2017}.
To better characterize the conjugacy relations in $R_0$, we introduce $C(r)$ defined in \cref{eq:cr}
of tuples $(i,j,k)$ such that $(i,j,k) \in C(r)$ if and only if $a_ia_ja_i = a_k$ is in $R_0$.

Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$, which is a nice conjugacy group defined in \cref{def:nice_conj_grp}.
The special property of $R_1$ is that every relation in $R_0$ can be recovered from $R_1$.
Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. 
It makes the construction of a finite-dimension representation of $\Gamma$ from
a finite-dimension representation of $\Pg_1$ easier.
Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
for each generator $a_i \in S_0$.
There is also a special generator $f_0 \in S_1$ such that
\begin{align*}
    a_i = b_ic_i = f_0d_i. 
\end{align*}
The relation $a_i = b_ic_i$ guarantees that $b_i$ commutes
with $c_i$.
The generators $b_i$ and $c_i$ are also related by a conjugacy relation
\begin{align*}
    c_i = f_0 b_i f_0. 
\end{align*}
For each $(i,j,k) \in C(r)$, 
$S_1$ contains an auxiliary generator $h_{jk}$, and
$R_1$ 
contains a conjugacy relation 
\begin{align*}
    d_ib_jd_i = c_k,
\end{align*}
and a linear relation
\begin{align*}
    h_{jk}b_jc_k = e.
\end{align*}
The introduction of $h_{jk}$ helps us to deduce that 
$b_j$ commutes with $c_k$.
Hence, every conjugacy relation in $R_1$ is either of the form
$f_0b_if_0 = c_i$ for $1 \leq i \leq r+5$, or
$d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
From the conjugacy relations in $R_1$, it can be proven that
\begin{align*}
    d_ic_jd_i = b_k \text{ for each } (i,j,k) \in C(r).
\end{align*}
Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
the conjugacy relations deduced above, so we can get
\begin{align*}
    a_ia_ja_i = f_0 d_i b_jc_j f_0 d_i
		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
		= (f_0 c_k f_0)(f_0 b_k f_0) 
		= b_k c_k = a_k.
\end{align*}
\carl{It would be good to explain (or at least reiterate) that these relations allow us to recover the conjugacy relations in $\mathcal{R}_0$.}
\hfc{I have added some explanation about the derivation. How does it look?}

@@

In the last step, we can construct $\Gamma:= \ip{S:R}$ with $S_1 \subset S$, in a way such that
$\Gamma$ only has linear relations, and the linear relations can be combined
to recover the conjugacy relations in $R_1$.
We demonstrate how relation $f_0 b_1 f_0 = c_1$ is embedded in
$6$ linear relations of $R$ as an example. 
We introduce auxiliary generators $f_1, f_2$ and $\{p_{1,j}\}_{j=1}^5$ such that they satisfy the linear relations:
\begin{align*}
    &f_0 f_1 f_2 = e && b_1 f_2 p_{1,1} = e && p_{1,1} p_{1,2} p_{1,3} = e\\
	&f_0 p_{1,3} p_{1,4} = e && c_1 p_{1,4} p_{1,5} = e \quad f_1 p_{1,2} p_{1,5} = e.
\end{align*}
Then, we expand $f_0b_1f_0$ by substituting in the equations above and
get
\begin{align*}
    f_0b_1f_0 = (f_1f_2)(f_2p_{1,1})(p_{1,3}p_{1,4}) =
    f_1 p_{1,2}p_{1,4} = p_{1,5}p_{1,4} = c_1.
\end{align*}
The other conjugacy relations of $\Pg_1$ are embedded in linear relations analogously.

A representation of $\Gamma$ can also be built upon
a representation $\Psi_1$ of $\Pg_1$, which is defined on
$\C^2 \x \calH$.
We denote the representation of $\Gamma$ by $\Psi$ and
it is defined on $\C^2 \x \C^2 \x \calH$ such that
\begin{align*}
    \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
    s \in S_1.
\end{align*}
In particular, it means that for each $a_i \in S_0$
\begin{align*}
    \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
\end{align*}
Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
by Lemma $15$ of Ref.~\cite{slofstra2017}.

%----------------------------------------
\subsection{Formal definitions}
\label{sec:gamma_def}
%----------------------------------------
We define the solution group of the linear system game $\LS(r)$ first, which is constructed following the steps
described in the previous subsection.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{J\} \cup \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
set of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ JsJs = e \vert s \in S\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
The group $\Gamma$ is a group with the presentation
$\ip{S:R}$.
\carl{[If you're really going to claim
that this is a complete definition, maybe you should write out the set $C$ somewhere as well?]}
\end{definition}
\hfc{I pointed out in the previous subsection that the definition of $C(r)$ is in the Appendix along with the definition of $\Pg_0$. 
Since $C(r)$ is defined by $\Pg_0$, a stand-alone definition of $C(r)$
will only confuse the reader. Are you suggesting that we don't make this a definition?}

@@

In the next three subsections, we analyze the implication of an approximate strategy for the 
three components introduced in \cref{sec:full_test}.

%------------------------------------------------------------------------------------------
\subsection{Implication of winning $\LS(r)$}
\label{sec:imp_lct}
%------------------------------------------------------------------------------------------
In the first half of this subsection, we use $(i,x(s))$ to denote the question pair so that Alice gets equation number $i$ and Bob gets a variable label $x(s)$ for some $s \in S$. For simplicity, we let Bob get the generator $s$ instead.
